Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-06-30 answer-to-reviewers.tex

\medskip
\emph{*** empirical analysis by Louis? give computation times for examples?\\
*** by considering only the parametric Beta distributions, we are already working with the extreme points of the credal set}
%in this continuous setting, the extreme points of the prior parameter set
%are the four Beta priors corresponding to combinations of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ with $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$,
%but the posterior parameter set is not convex
%
%most work by Alessio Benavoli concerns near-noninformative sets of priors, while we deal with ***
\medskip

\textbf{Existing work}\\
Another point to be addressed by the authors in the final version is the existing work in the field. Some pointers about reliability analysis with IPs can be found in many papers by Christophe Simon (within the framework of evidence theory) and Didier Dubois (within the framework of possibilistic theory) as well as in the paper about the imprecise noisy-OR gate by Alessandro Antonucci (withing the framework of credal sets and networks). Some words should be also spent about the independence assumptions in the underlying model. It is true that the discussion here is very general, but the specific notion of independence might have a strong impact on the corresponding complexity of the inferences. Moreover, Gert de Cooman has some papers on the impact of the exchangeability assumption on imprecise probabilistic models. The relation with the current model also deserves some comment.

\medskip
\emph{We now refer to existing work in the introduction section and clarify the contribution of our work.
In Section~6, we now also state clearly the assumptions regarding independence and exchangeability
underlying our imprecise probability model.}
\medskip

@@

\textbf{Presentation}\\
- The core of the paper is (in my opinion) S6 and, more specifically, E10. I would give more emphasis to this result and also to LM3 which is crucial as well as TH2 (while TH1 is more a preparatory result. In the proofs of both Th 1 and Th 2 some results from [18] and [15] are cited. I would better shape them as preparatory lemmas (with no need of explicit proof, but with an explicit statement). This would be a chance to explicitly formalize the two notions of dominance considered here. I would also remove the first part of the proof of Th 2 by saying that it is totally analogous to that of Th 1.

\medskip
\emph{We do not see Theorem~1 as preparatory result, but as equally essential as Theorem~2 and Lemma~3
for ensuring the tractability of our approach.
We also do not feel that writing out the definitions of first-order stochastic dominance and likelihood ratio order is necessary,
as the former is a standard notion, and the latter is made explicit within the proof of Theorem~1.
We thus prefer to leave presentation here as it is.}
\medskip

@@

- The expression ''in an arbitrarily fine grid of time points'' in the introduction might sound a bit obscure

\medskip
\emph{We wanted to express here that there are no restrictions on time grid density,
and do not see the need to phrase this otherwise.}
\medskip

@@

- \verb+\overline{x}+ for arrays might be a bit confusive in a IP paper, why not to use \verb+\vec{}+ or \verb+\bm{}+?

\medskip
\emph{We changed the notation in Section~2 to use $\vec{x}$ in place of $\underline{x}$ for state vectors.}
\medskip

@@

- The term 'natural extension' at page 6 should be clarified

\medskip
\emph{To avoid confusion with the notion of `natural extension' from imprecise probability literature,
we changed the wording to `simple extension' here.}
\medskip

@@

- Typo in ''$p_t^k$,s can''(page 6)

\medskip
\emph{We now write `The sequence of $\ptk$'s can, in theory, be directly chosen \ldots' to emphasize the plural here.}
\medskip

@@

- $n^{(n)}$ is weird (page 7)

\medskip
\emph{Agreed, but we wish to be consistent with previous literature on sets of conjugate priors and so prefer to keep this notation.}
\medskip

@@

- Sec 4, why not to cite that the re-parametrization is based on the re-parametrization a' la Walley for the Dir distribution?

\medskip
\emph{***Walley uses this parametrization for the IDM / IBM, but it has been known before that as natural or canonical parametrization, ***}
\medskip

@@

- I would shape the example at the end of S4 in an example environment

\medskip
\emph{***}
\medskip

- I see the issues related to the improper priors in the vacuous case, yet in the discussion of this issue I miss a link with Walley's IDM (or IBM \ldots).

### 2016-06-30 ijar-npb-ms.tex
addressing reviewer 1 cont.

In the mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
of its components and the structure of the system. The mathematical concept which is central to this theory is the 
\emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
$\underline{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\underline{x}$. 
The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\underline{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\underline{x}$. 
Most practical systems are coherent, which means that $\phi(\underline{x})$ 
is non-decreasing in any of the components of $\underline{x}$, so system functioning cannot be improved by worse performance 
of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
quantification for system reliability. It is further logical to assume that $\phi(\underline{0})=0$ and $\phi(\underline{1})=1$, 
so the system fails if all its components fail and it functions if all its components function.

@@

Consider a system with $K\ge 1$ types of components, with $m_k$ components of type $k \in \{1,\ldots,K\}$ and 
$\sum_{k=1}^K m_k = m$. Assume that the random failure times of components of the same type are exchangeable \citep{DF74}.
Due to the arbitrary ordering of the components in the state vector, components of the same type can be grouped together, 
leading to a state vector that can be written as 
$\underline{x} = (\underline{x}^1,\underline{x}^2,\ldots,\underline{x}^K)$, with 
$\underline{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.

@@

For calculating the survival signature based on the structure function, observe that
there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}
%
%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
%Then, for system failure time $\Tsys$,
%\begin{align*}
%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
%\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \cite{CCM15}. %\citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}
We will employ both assumptions in this paper,
leading to $C^k_t$ having a Beta-Binomial distribution,
giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.

@@

The set of probabilities $\{ \ptk, t \in {\cal T}\}$
defines a discrete failure time distribution for components of type $k$ through
\begin{align*}
R^k(t_j) &= P(T^k > t_j) = p^k_{t_j},\ t_j = t_1, \ldots, \tmax\,.
\end{align*}
We can also express this failure time distribution through the probability mass function (pmf) and discrete hazard function,
\begin{align*}
f^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\big) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
h^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\mid T^k > t_j\big) = \frac{f^k(t_j)}{R^k(t_j)}\,. % or R^k(t_{j-1}) ???
\end{align*}
The time grid $\cal T$ can be chosen to be appropriately dense for the application at hand,
with the natural extension between grid points by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
or by taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.

@@

The $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
$[0,\infty)$, for example matching a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
However, such direct specification is non-trivial, neglects any inherent uncertainty in the particular choice, and cannot be 
easily combined with test data.
To account for the uncertainty, one can express knowledge about $\ptk$ through a prior distribution.
A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, particularly because in a Bayesian inferential
setting this is the conjugate prior which leads to a Beta posterior.

>>>>

In the mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
of its components and the structure of the system. The mathematical concept which is central to this theory is the 
\emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
$\vec{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\vec{x}$. 
The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$. 
Most practical systems are coherent, which means that $\phi(\vec{x})$ 
is non-decreasing in any of the components of $\vec{x}$, so system functioning cannot be improved by worse performance 
of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
quantification for system reliability. It is further logical to assume that $\phi(\vec{0})=0$ and $\phi(\vec{1})=1$, 
so the system fails if all its components fail and it functions if all its components function.

@@

Consider a system with $K\ge 1$ types of components, with $m_k$ components of type $k \in \{1,\ldots,K\}$ and 
$\sum_{k=1}^K m_k = m$. Assume that the random failure times of components of the same type are exchangeable \citep{DF74}.
Due to the arbitrary ordering of the components in the state vector, components of the same type can be grouped together, 
leading to a state vector that can be written as 
$\vec{x} = (\vec{x}^1,\vec{x}^2,\ldots,\vec{x}^K)$, with 
$\vec{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.

@@

For calculating the survival signature based on the structure function, observe that
there are $\binom{m_k}{l_k}$ state vectors $\vec{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\vec{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\vec{x} \in S_{l_1,\ldots,l_K}} \phi(\vec{x})\,.
\end{align}
%
%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
%Then, for system failure time $\Tsys$,
%\begin{align*}
%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
%\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \cite{CCM15}. %\citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}
We will employ both assumptions in this paper,
leading to $C^k_t$ having a Beta-Binomial distribution,
giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.

@@

The set of probabilities $\{ \ptk, t \in {\cal T}\}$
defines a discrete failure time distribution for components of type $k$ through
\begin{align*}
R^k(t_j) &= P(T^k > t_j) = p^k_{t_j},\ t_j = t_1, \ldots, \tmax\,.
\end{align*}
We can also express this failure time distribution through the probability mass function (pmf) and discrete hazard function,
\begin{align*}
f^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\big) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
h^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\mid T^k > t_j\big) = \frac{f^k(t_j)}{R^k(t_j)}\,. % or R^k(t_{j-1}) ???
\end{align*}
The time grid $\cal T$ can be chosen to be appropriately dense for the application at hand,
where a simple extension between grid points can be made by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
or by taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.

@@

The sequence of $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
$[0,\infty)$, for example matching a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
However, such direct specification is non-trivial, neglects any inherent uncertainty in the particular choice, and cannot be 
easily combined with test data.
To account for the uncertainty, one can express knowledge about $\ptk$ through a prior distribution.
A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, particularly because in a Bayesian inferential
setting this is the conjugate prior which leads to a Beta posterior.
